### 2014-10-24 intro.tex
Merged changes in intro

Many real-world web applications --- such as Amazon, Facebook, Google, Twitter
--- replicate application state and logic across multiple \emph{replicas} within
and across data centers. Replication is intended not only to improve application
throughput and reduce user perceived latency, but also to tolerate partial
failures without compromising the service availability. Traditionally
programmers have relied on \emph{strong consistency} guarantees, such as
Linerizability~\cite{Herlihy1990} or serializability~\cite{Serializability},
provided by the underlying data store in order to build correct applications.
While strong consistency is simple to reason about, the CAP
theorem~\cite{Brewer2000,Gilbert} makes it impossible for a replicated data
store to achieve strong consistency, while tolerating network partitions and
remaining highly available. Thus, modern web applications, which aim to provide
an "always on" experience, overwhelmingly embrace availability and partition
tolerance at the expense of strong consistency.

@@

Moreover, weak consistency hinders compositional reasoning about programs.
While applications are usually built around rich abstract data types, such as
dictionaries, counters, queues, and graphs, geo-distributed stores typically
only provide a minimal set of data types with in-built conflict resolution
strategy such as last-writer-wins (LWW) register, counters and
sets~\cite{Cassandra,DynamoDB}.  While traditional database systems enable
composability through transactions, the state-of-the-art geo-distributed stores
lack unrestricted transactional access to the data. Indeed, traditional database
systems do offer a variety of transaction isolation levels~\cite{}, each with a
particular runtime overhead, leaving the choice of correct consistency level to
the programmer. Thus, the programmer working with geo-distributed stores has but
to coerce the application state to the data store capabilities.

@@

\item We introduce Quelea, a language for declaratively describing eventually
consistent programs. Replicated data types in Quelea are defined as reductions
over the set of previously seen updates on an object; new updates are simply
appended to this set. Quelea is equipped with a contract language to describe
fine-grained application-level consistency properties. The contracts are
logically analyzed, and the corresponding operations are automatically assigned
to the most efficient store consistency level under which the application-level
contracts are guaranteed to hold.

\item Quelea supports coordination-free transactions over arbitrary datatypes.
We extend our contract language to express fine-grained transaction isolation
guarantees, and utilize the contract enforcement system to automatically assign
the correct and most efficient isolation level for a transaction.

\item We present meta-theory that certifies the soundness of our contract
enforcement system, and ensures that an operation is only executed if the
required conditions on consistency are met.

\item Quelea is implemented as a shim layer over (and importantly without
modifying) Cassandra, a general-purpose data store, illustrating the
portability of our approach. An extensive experimental evaluation over a
collection of real-world applications, including a Twitter-like micro-blogging
site and an ebay-like auction site illustrates the practicality of our
approach.

@@

The rest of the paper is organized as follows. Section~\ref{sec:motivation}
motivates Quelea and introduces the language through a series of examples.
Section~\ref{sec:lang} presents the contract language, and
section~\ref{sec:opsem} presents the operational semantics of the Quelea
runtime system. Section~\ref{sec:txns} introduces transaction contracts and
classification. Section~\ref{sec:impl} describes the implementation and goes
into detail about the optimizations needed to make the system practical.
Section~\ref{sec:results} present the experimental evaluation.
Section~\ref{sec:related} and~\ref{sec:concl} discuss the related work and
conclusions.

>>>>

Many real-world web applications --- such as Amazon, Facebook, Google, Twitter
--- replicate application state and logic across multiple \emph{replicas} within
and across data centers. Replication is intended not only to improve application
throughput and reduce user perceived latency, but also to tolerate partial
failures without compromising the service availability. Traditionally
programmers have relied on \emph{strong consistency} guarantees, such as
Linerizability~\cite{Herlihy1990} or serializability~\cite{Serializability},
provided by the underlying data store in order to build correct applications.
While strong consistency is an easily stated property, it
masks the reality underlying large-scale distributed systems with respect to
non-uniform latency (i.e., availability) and network
partitions~\cite{Brewer2000,Gilbert}. Indeed, modern web applications, which aim to provide
an "always on" experience, overwhelmingly embrace availability and partition
tolerance at the expense of strong consistency.

@@

Moreover, weak consistency hinders compositional reasoning about programs.
While an application might be naturally expressed in terms of well-understood
abstract data types, such as dictionaries, counters, queues, and graphs,
geo-distributed stores typically only provide a minimal set of data types with
in-built conflict resolution strategy such as last-writer-wins (LWW) registers,
counters and sets~\cite{Cassandra,DynamoDB}.  Furthermore, while traditional
database systems enable composability through transactions, existing
geo-distributed stores lack unrestricted transactional access to the data.
Working with geo-distributed stores thus requires application state to be
suitably coerced to work within the capabilities of the store.

@@

\item We introduce \name, a language for declaratively describing eventually
  consistent programs that manipulate replicated data types. Contracts are
  used to specify fine-grained application-level consistency properties, and
  are analyzed to assign the most efficient and sound store consistency
  level to the corresponding operation.

\item \name supports coordination-free transactions over arbitrary
  datatypes.  We extend our contract language to express fine-grained
  transaction isolation guarantees, and utilize the contract enforcement
  system to automatically assign the correct and most efficient isolation
  level for a transaction.

\item Metatheory that certifies the soundness of our contract enforcement
  system, and ensures that an operation is only executed if the required
  conditions on consistency are met is also given.

\item \name is implemented as a shim layer over (and importantly without
  modifying) Cassandra, a well-known general-purpose data store.  An
  extensive experimental evaluation over a collection of real-world
  applications, including a Twitter-like micro-blogging site and an
  eBay-like auction site illustrates the practicality of our approach.

@@

The rest of the paper is organized as follows. Section~\ref{sec:motivation}
motivates \name and introduces the language through a series of examples.
Section~\ref{sec:lang} describes the contract language, and
Section~\ref{sec:opsem} presents an operational semantics.
Section~\ref{sec:txns} introduces transaction contracts and
classification. Section~\ref{sec:impl} describes the implementation and goes
into detail about the optimizations needed to make the system practical.
Section~\ref{sec:results} discusses experimental evaluation.
Section~\ref{sec:related} and~\ref{sec:concl} present related work and
conclusions.
